---
title: "Meeting Title"
meeting-type: "Committee Meeting"  # e.g., "Faculty Meeting", "Project Standup", "Advisory Board"
date: today
time: "2:00 PM - 3:00 PM"
location: "ENR2 Room 123 / Zoom"
zoom-link: "https://arizona.zoom.us/j/123456789"

chair: "Chair Name"
note-taker: "Note Taker Name"

attendees:
  - name: "Person One"
    role: "Chair"
  - name: "Person Two"
    role: "Member"
  - name: "Person Three"
    role: "Member"
  - name: "Person Four"
    role: "Guest"

agenda-items:
  - topic: "Call to Order & Approval of Minutes"
    duration: "5 min"
    presenter: "Chair"
    notes: ""
  - topic: "Old Business"
    duration: "15 min"
    presenter: "Various"
    notes: "Follow up on action items from last meeting"
  - topic: "New Business Item 1"
    duration: "20 min"
    presenter: "Person Two"
    notes: "Description of the topic to be discussed"
  - topic: "New Business Item 2"
    duration: "15 min"
    presenter: "Person Three"
    notes: ""
  - topic: "Open Discussion"
    duration: "10 min"
    presenter: "All"
    notes: ""
  - topic: "Action Items & Adjournment"
    duration: "5 min"
    presenter: "Chair"
    notes: ""

format:
  typst:
    papersize: us-letter
    margin:
      top: 0.75in
      bottom: 0.75in
      left: 0.75in
      right: 0.75in
    fontsize: 10pt
    mainfont: "Times New Roman"
  html:
    toc: false
    embed-resources: true
    theme:
      - cosmo
      - infosci-agenda.scss
---

```{=typst}
// Meeting header
#align(center)[
  #text(size: 18pt, fill: rgb("#0C234B"), weight: "bold")[{{< meta title >}}]

  #text(size: 12pt, fill: rgb("#AB0520"))[{{< meta meeting-type >}}]

  #v(0.1in)

  #text(size: 10pt)[
    *Date:* {{< meta date >}} \
    *Time:* {{< meta time >}} \
    *Location:* {{< meta location >}}
  ]
]

#line(length: 100%, stroke: 1pt + rgb("#0C234B"))
#v(0.15in)
```

::: {.grid}
::: {.g-col-6}
**Chair:** {{< meta chair >}}

**Note Taker:** {{< meta note-taker >}}
:::
::: {.g-col-6}
**Zoom:** [Join Meeting]({{< meta zoom-link >}})
:::
:::

## Attendees

```{r}
#| echo: false
#| output: asis

attendees <- rmarkdown::metadata$attendees
if (!is.null(attendees)) {
  cat("| Name | Role |\n|------|------|\n")
  for (a in attendees) {
    cat(sprintf("| %s | %s |\n", a$name, a$role))
  }
}
```

## Agenda

```{r}
#| echo: false
#| output: asis

items <- rmarkdown::metadata$`agenda-items`
if (!is.null(items)) {
  cat("| # | Topic | Duration | Presenter | Notes |\n")
  cat("|---|-------|----------|-----------|-------|\n")
  for (i in seq_along(items)) {
    item <- items[[i]]
    notes <- if (is.null(item$notes) || item$notes == "") "" else item$notes
    cat(sprintf("| %d | %s | %s | %s | %s |\n",
                i, item$topic, item$duration, item$presenter, notes))
  }
}
```

## Minutes

*Notes from the meeting:*

### Item 1: [Topic]

- Discussion point
- Discussion point
- **Decision:** [What was decided]

### Item 2: [Topic]

- Discussion point
- Discussion point

## Action Items

| Action | Assignee | Due Date | Status |
|--------|----------|----------|--------|
| Action item description | Person | Date | ⬜ Pending |
| Action item description | Person | Date | ⬜ Pending |
| Action item description | Person | Date | ⬜ Pending |

## Next Meeting

**Date:** [Next meeting date]
**Time:** [Time]
**Location:** [Location]

---

*Minutes prepared by {{< meta note-taker >}} on {{< meta date >}}*
